PoVaTiM: A Possibilistic Valid-Time Model \\ \vspace*{0.04truein}

### 2012-04-05 ijcis-pos-model/sources/temporalModel.tex
Preliminary version for the ijcis paper

\subsection{\label{subsec:time-interval-constraint}The time interval}
The representation of a temporal interval is given by two points: S the starting and E the ending points respectively.

\vglue13pt
%\begin{table}[htbp]
\tcap{Data types for a time point}
\centerline{\small DATA TYPES}
\vglue-6pt
\centerline{\small\baselineskip=13pt
\begin{tabular}{c p{2cm} p{2cm}}\\
\hline
1 & A single time point &  $1/x, x \in \T$\\
2 & A possibility distribution in the numeric domain & A fuzzy number or a fuzzy interval.\\
3 & An unknown value & \textbf{UNKNOWN}$= \lbrace1/t, t \in \T \rbrace$\\
4 & An undefined value & \textbf{UNDEFINED}$= \lbrace 0/t, t \in \T \rbrace$\\
5 & A null value & \textbf{NULL} $=\lbrace 1/$Unknown, 1/Undefined $\rbrace$\\
\hline\\
\end{tabular}
\label{tbl:time-point-types}
}
%\end{table}

\textcolor{red}{MAYBE COMPATIBILITY WITH GEFRED TYPES??}

A valid temporal interval $\left[S,E\right]$ in the system is a combination for the values of $S$,$E$ as shown in table \ref{tbl:valid-time-interval}.

\textcolor{red}{HAS IT ANY SENSE TO ALLOW THE COMBINATION [UNKNOWN, UNDEFINED] AND SO ON??}

\vglue13pt
%\begin{table}[htbp]
\tcap{Valid-Time interval data types}
\centerline{\small VALID TIME DATA TYPES}
\vglue-6pt
\centerline{\small\baselineskip=13pt
\begin{tabular}{c p{2cm} p{2cm}}\\
\hline
Type for S & Type for E & Semantics \\
\hline
Unknown & Unkown & Unknown interval. \\
Undefined & Undefined & Undefined interval. \\
Null & Null & Null interval. \\
\hline
1,2 & 1,2 & A possibilistic time interval. \\
\hline\\
\end{tabular}
\label{tbl:valid-time-interval}}
%\end{table}

>>>>

\vglue13pt
%\begin{table}[htbp]
\tcap{Valid-Time interval data types}
\centerline{\small VALID TIME DATA TYPES}
\vglue-6pt
\centerline{\small\baselineskip=13pt
\begin{tabular}{c p{2cm} p{2cm}}\\
\hline
Type for S & Type for E & Semantics \\
\hline
Unknown & Unkown & Unknown interval. \\
\hline
1,2 & 1,2 & A possibilistic time interval. \\
\hline\\
\end{tabular}
\label{tbl:valid-time-interval}}
%\end{table}
